---
title: 'PanRank - Genes4Epilepsy'
css: styles.css
---
[Jacob E. Munro](https://orcid.org/0000-0002-2751-0989), [Mark F.
Bennett](https://orcid.org/0000-0002-3561-6804), [Melanie
Bahlo](https://orcid.org/0000-0001-5132-0774)

---

[Genes4Epilepsy](https://doi.org/10.1111/epi.17547) is a curated list
of monogenic epilepsy genes.

This page contains **PanRank** candidate gene
rankings based on gene panels from
[Genes4Epilepsy](https://bahlolab.github.io/Genes4Epilepsy/). PanRank scores are
between 0 and 1 and represent the predicted probability that a gene is
disease-causing with the specified mode of inheritance. The "Known Inheritance"
column indicates the known mode of inheritance used to train the model.  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)

make_select_script <- function(named_files, label) {
  str_c(
    '<script>',
    'function makeSelect() {',
    str_c('return \'<label for="file-select">', label, ':</label>\' +'),
    '\'<select id="file-select" class="custom-select">\' +',
    str_c('\'<option value="', named_files, '">', names(named_files), '</option> \' +', collapse = '\n'),
    '\'</select>\';',
    '}',
    '</script>',
    sep = '\n'
  )
}

make_doc_ready_script <- function(fixedUrl, initUrl) {
  str_c(
    '<script>',
    '$(document).ready(function() {',
    str_c('const fixedUrl = "', fixedUrl, '";'),
    str_c('const initUrl = "', initUrl, '";'),
    'loadData(fixedUrl, initUrl);',
    '});',
    '</script>',
    sep = '\n'
  )
}
```

```{r, results='asis'}
files <-
  list.files('data', pattern = '.csv.gz$', full.names = T) %>%
  keep(str_detect, 'G4E_') %>%
  discard(str_detect, "fixed.csv.gz") %>%
  setNames(., str_remove(basename(.), '.csv.gz$'))

names(files) <-
  names(files) %>%
  str_remove('G4E_') %>%
  str_replace('ALL', 'Epilepsy')

cat(
  read_file(
    'template.html'
  ),
  
  make_select_script(
    named_files = files,
    label = 'Phenotype'
  ),
  
  make_doc_ready_script(
    fixedUrl = "data/fixed.csv.gz",
    initUrl = files[1]
  )
)
```


**Note:** "GGE" and "Focal" phenotypes have insufficient numbers of recessively inherited genes for training so no predictions are made.